---
title: "Survey Daily Report"
date: "`r format(Sys.time(), '%B %d, %Y %H:%M')`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float:
      collapsed: false
    toc_depth: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(kableExtra)
library(ggspatial)
library(gridExtra)

source("hh_cleanup.R")
source("ws_cleanup.R")
```

```{r select_columns}
hh_daily <- hh_data %>%
  select(uuid, community, zone, hhid, surveyor_name, resp_surveyor,
         survey_date, survey_month,
         name, number, gps_location)

ws_daily <- ws_data %>%
  select(uuid, wsid, community, zone, surveyor_name,
         survey_date, display_month, gps_location,
         respondent_name, water_source_type)
```

```{r subsets}
hh_current <- hh_daily %>%
  filter(survey_date >= floor_date(Sys.Date(), "month"))

ws_current <- ws_daily %>%
  filter(survey_date >= floor_date(Sys.Date(), "month"))
```

```{r targets}
surveyor_targets <- hh_daily %>%
  filter(!is.na(hhid)) %>%
  distinct(hhid, resp_surveyor) %>%
  count(resp_surveyor, name = "target") %>%
  filter(!resp_surveyor %in% c("Unknown"))

current_month_hhids <- hh_current %>%
  filter(!is.na(hhid)) %>%
  distinct(hhid)

surveyor_completed <- hh_daily %>%
  filter(!is.na(hhid)) %>%
  distinct(hhid, resp_surveyor) %>%
  filter(hhid %in% current_month_hhids$hhid) %>%
  count(resp_surveyor, name = "completed")

surveyor_progress <- surveyor_targets %>%
  left_join(surveyor_completed, by = "resp_surveyor") %>%
  replace_na(list(completed = 0)) %>%
  mutate(remaining = target - completed)
```

**Total**: `r sum(surveyor_progress$completed)`/`r sum(surveyor_progress$target)` surveys completed, **`r sum(surveyor_progress$remaining)`** remaining

**Abdulai K**: `r surveyor_progress$completed[surveyor_progress$resp_surveyor == "Abdulai K"]`/`r surveyor_progress$target[surveyor_progress$resp_surveyor == "Abdulai K"]` surveys completed, **`r surveyor_progress$remaining[surveyor_progress$resp_surveyor == "Abdulai K"]`** remaining

**Jamiatu**: `r surveyor_progress$completed[surveyor_progress$resp_surveyor == "Jamiatu"]`/`r surveyor_progress$target[surveyor_progress$resp_surveyor == "Jamiatu"]` surveys completed, **`r surveyor_progress$remaining[surveyor_progress$resp_surveyor == "Jamiatu"]`** remaining

**Boboieh**: `r surveyor_progress$completed[surveyor_progress$resp_surveyor == "Boboieh"]`/`r surveyor_progress$target[surveyor_progress$resp_surveyor == "Boboieh"]` surveys completed, **`r surveyor_progress$remaining[surveyor_progress$resp_surveyor == "Boboieh"]`** remaining

**Musa**: `r surveyor_progress$completed[surveyor_progress$resp_surveyor == "Musa"]`/`r surveyor_progress$target[surveyor_progress$resp_surveyor == "Musa"]` surveys completed, **`r surveyor_progress$remaining[surveyor_progress$resp_surveyor == "Musa"]`** remaining

# Recent Performance

```{r recent-performance}
all_dates <- sort(unique(c(hh_current$survey_date, ws_current$survey_date)), decreasing = TRUE)

hh_counts <- hh_current %>%
  count(surveyor_name, survey_date, name = "n_hh")

ws_counts <- ws_current %>%
  count(surveyor_name, survey_date, name = "n_source")

combined_raw <- hh_counts %>%
  full_join(ws_counts, by = c("surveyor_name", "survey_date")) %>%
  replace_na(list(n_hh = 0, n_source = 0)) %>%
  mutate(n_total = n_hh + n_source)

week_totals <- hh_current %>%
  filter(survey_date >= Sys.Date() - 7) %>%
  count(surveyor_name, name = "hh_week") %>%
  full_join(
    ws_current %>%
      filter(survey_date >= Sys.Date() - 7) %>%
      count(surveyor_name, name = "source_week"),
    by = "surveyor_name"
  ) %>%
  replace_na(list(hh_week = 0, source_week = 0))

month_totals <- hh_current %>%
  filter(survey_date >= Sys.Date() - 30) %>%
  count(surveyor_name, name = "hh_month") %>%
  full_join(
    ws_current %>%
      filter(survey_date >= Sys.Date() - 30) %>%
      count(surveyor_name, name = "source_month"),
    by = "surveyor_name"
  ) %>%
  replace_na(list(hh_month = 0, source_month = 0))

combined <- combined_raw %>%
  complete(surveyor_name, survey_date = all_dates, fill = list(n_hh = 0, n_source = 0, n_total = 0)) %>%
  left_join(week_totals, by = "surveyor_name") %>%
  left_join(month_totals, by = "surveyor_name") %>%
  replace_na(list(hh_week = 0, source_week = 0, hh_month = 0, source_month = 0)) %>%
  arrange(surveyor_name) %>%
  filter(rowSums(across(where(is.numeric)), na.rm = TRUE) > 0)

# Community subtotal helper
make_subtotal <- function(hh, ws, comm = NULL, label) {
  hh_f <- if (!is.null(comm)) filter(hh, community == comm) else hh
  ws_f <- if (!is.null(comm)) filter(ws, community == comm) else ws
  
  daily <- hh_f %>%
    count(survey_date, name = "n_hh") %>%
    full_join(ws_f %>% count(survey_date, name = "n_source"), by = "survey_date") %>%
    replace_na(list(n_hh = 0, n_source = 0))
  
  daily %>%
    mutate(
      n_total = n_hh + n_source,
      count_text = paste0("(", n_hh, " hh / ", n_source, " ws)"),
      surveyor_name = label,
      hh_week = nrow(filter(hh_f, survey_date >= Sys.Date() - 7)),
      source_week = nrow(filter(ws_f, survey_date >= Sys.Date() - 7)),
      hh_month = nrow(filter(hh_f, survey_date >= Sys.Date() - 30)),
      source_month = nrow(filter(ws_f, survey_date >= Sys.Date() - 30))
    ) %>%
    select(surveyor_name, survey_date, count_text, n_total, hh_week, source_week, hh_month, source_month)
}

grand_total <- make_subtotal(hh_current, ws_current, NULL, "GRAND TOTAL")
portee_subtotal <- make_subtotal(hh_current, ws_current, "Portee Rokupa", "Portee Rokupa Total")
dworzark_subtotal <- make_subtotal(hh_current, ws_current, "Dworzark", "Dworzark Total")
cockle_subtotal <- make_subtotal(hh_current, ws_current, "Cockle Bay", "Cockle Bay Total")

# Color function
apply_color <- function(text, n_total, date) {
  if (is.na(n_total) || n_total == 0) return("")
  is_weekend <- weekdays(date) %in% c("Saturday", "Sunday")
  if (is_weekend) {
    if (n_total > 10) paste0('<span style="background-color: #ccffcc; display: block;">', text, '</span>')
    else text
  } else {
    case_when(
      n_total < 8 ~ paste0('<span style="background-color: #ffcccc; display: block;">', text, '</span>'),
      n_total > 10 ~ paste0('<span style="background-color: #ccffcc; display: block;">', text, '</span>'),
      TRUE ~ text
    )
  }
}

dates_to_show <- all_dates[1:min(4, length(all_dates))]

combined_final <- combined %>%
  mutate(count_text = ifelse(n_total > 0, paste0("(", n_hh, " hh / ", n_source, " ws)"), "")) %>%
  select(surveyor_name, survey_date, count_text, n_total, hh_week, source_week, hh_month, source_month) %>%
  bind_rows(grand_total, portee_subtotal, dworzark_subtotal, cockle_subtotal) %>%
  mutate(
    count_text = mapply(apply_color, count_text, n_total, survey_date),
    totals = paste0(
      "Week: ", hh_week, " hh / ", source_week, " ws<br>",
      "Month: ", hh_month, " hh / ", source_month, " ws"
    ),
    surveyor_name = factor(
      surveyor_name,
      levels = c(
        "GRAND TOTAL",
        "Abdulai K", "Abdulai B", "Portee Rokupa Total",
        "Jamiatu", "Boboieh", "Sinneh", "Joseph", "Moses", "Dworzark Total",
        "Musa", "Joana", "Cockle Bay Total", "Other"
      )
    )
  ) %>%
  arrange(surveyor_name) %>%
  select(surveyor_name, totals, survey_date, count_text) %>%
  pivot_wider(names_from = survey_date, values_from = count_text, values_fill = "") %>%
  select(surveyor_name, totals, all_of(as.character(dates_to_show)))

sunday_cols <- which(weekdays(as.Date(dates_to_show)) == "Sunday") + 2

tbl <- combined_final %>%
  kable(
    col.names = c("Surveyor", "Totals", format(dates_to_show, "%a %b %d")),
    escape = FALSE, format = "html",
    align = c("l", "c", rep("c", length(dates_to_show)))
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE, position = "left", fixed_thead = TRUE
  ) %>%
  row_spec(
    which(combined_final$surveyor_name %in%
            c("GRAND TOTAL", "Portee Rokupa Total", "Dworzark Total", "Cockle Bay Total")),
    bold = TRUE, background = "#f0f0f0",
    extra_css = "white-space: nowrap; vertical-align: middle;"
  ) %>%
  row_spec(0, extra_css = "white-space: nowrap;") %>%
  column_spec(2:ncol(combined_final), extra_css = "white-space: nowrap; vertical-align: middle;") %>%
  column_spec(2, extra_css = "border-right: 2px solid black; white-space: nowrap; vertical-align: middle;")

for (col in sunday_cols) {
  tbl <- tbl %>% column_spec(col, extra_css = "border-left: 2px solid black; white-space: nowrap; vertical-align: middle;")
}

tbl
```

# Mapping
```{r map_setup}
# Shapefiles already loaded from cleanups - create 4326 versions for display
cockle_4326 <- st_transform(cockle_shapefile, 4326)
dworzark_4326 <- st_transform(dworzark_shapefile, 4326)
portee_4326 <- st_transform(portee_shapefile, 4326)

buffer_distances <- c("Portee Rokupa" = 100, "Dworzark" = 100, "Cockle Bay" = 200)
```

```{r map_function}
surveyor_map <- function(selected_surveyor) {
  current_month <- month(Sys.Date())
  current_year <- year(Sys.Date())
  include_water_sources <- current_month %in% c(11, 1, 3, 5, 7, 9)
  
  # Get this surveyor's target HHIDs
  surveyor_hhids <- hh_daily %>%
    filter(!is.na(hhid), resp_surveyor == selected_surveyor) %>%
    distinct(hhid) %>%
    pull(hhid)
  
  # Get communities this surveyor works in
  surveyor_communities <- hh_daily %>%
    filter(hhid %in% surveyor_hhids) %>%
    pull(community) %>%
    unique()
  
  # Collect shapefiles for relevant communities
  shapefiles_list <- list()
  if ("Cockle Bay" %in% surveyor_communities) shapefiles_list$cockle <- cockle_4326
  if ("Portee Rokupa" %in% surveyor_communities) shapefiles_list$portee <- portee_4326
  if ("Dworzark" %in% surveyor_communities) shapefiles_list$dworzark <- dworzark_4326
  
  # Helper: get UTM shapefile by community name
  get_utm <- function(comm) {
    switch(as.character(comm),
           "Cockle Bay" = cockle_shapefile_utm,
           "Portee Rokupa" = portee_shapefile_utm,
           "Dworzark" = dworzark_shapefile_utm)
  }
  
  # Helper: filter sf points within buffer distance of their community shapefile
  filter_within_buffer <- function(sf_data) {
    if (nrow(sf_data) == 0) return(sf_data)
    sf_utm <- st_transform(sf_data, crs = 32628)
    keep <- rep(FALSE, nrow(sf_utm))
    for (i in seq_len(nrow(sf_utm))) {
      comm <- as.character(sf_utm$community[i])
      utm_shp <- get_utm(comm)
      if (!is.null(utm_shp)) {
        dist <- as.numeric(st_distance(sf_utm[i, ], utm_shp))
        keep[i] <- dist <= buffer_distances[comm]
      }
    }
    sf_data[keep, ]
  }
  
  # --- HOUSEHOLDS ---
  surveyor_hh_current <- hh_daily %>%
    filter(hhid %in% surveyor_hhids,
           month(survey_date) == current_month,
           year(survey_date) == current_year,
           !is.na(gps_location)) %>%
    separate(gps_location, into = c("latitude", "longitude", "altitude", "accuracy"),
             sep = " ", remove = FALSE, convert = TRUE) %>%
    filter(!is.na(latitude), !is.na(longitude)) %>%
    st_as_sf(coords = c("longitude", "latitude"), crs = 4326)
  
  surveyor_hh_current <- filter_within_buffer(surveyor_hh_current) %>%
    mutate(
      category = case_when(
        survey_date == Sys.Date() ~ "HH Today",
        survey_date == Sys.Date() - 1 ~ "HH Yesterday",
        TRUE ~ "HHs Completed"
      )
    )
  
  current_hhids <- unique(surveyor_hh_current$hhid)
  
  surveyor_hh_unmapped <- hh_daily %>%
    filter(hhid %in% surveyor_hhids,
           !hhid %in% current_hhids,
           !is.na(gps_location)) %>%
    group_by(hhid) %>%
    arrange(desc(survey_date)) %>%
    slice(1) %>%
    ungroup() %>%
    separate(gps_location, into = c("latitude", "longitude", "altitude", "accuracy"),
             sep = " ", remove = FALSE, convert = TRUE) %>%
    filter(!is.na(latitude), !is.na(longitude)) %>%
    st_as_sf(coords = c("longitude", "latitude"), crs = 4326)
  
  surveyor_hh_unmapped <- filter_within_buffer(surveyor_hh_unmapped) %>%
    mutate(category = "HH To Do")
  
  # --- WATER SOURCES ---
  if (include_water_sources) {
    surveyor_ws_current <- ws_daily %>%
      filter(community %in% surveyor_communities,
             month(survey_date) == current_month,
             year(survey_date) == current_year,
             !is.na(gps_location)) %>%
      separate(gps_location, into = c("latitude", "longitude", "altitude", "accuracy"),
               sep = " ", remove = FALSE, convert = TRUE) %>%
      filter(!is.na(latitude), !is.na(longitude)) %>%
      st_as_sf(coords = c("longitude", "latitude"), crs = 4326)
    
    surveyor_ws_current <- filter_within_buffer(surveyor_ws_current) %>%
      mutate(
        category = case_when(
          survey_date == Sys.Date() ~ "WS Today",
          survey_date == Sys.Date() - 1 ~ "WS Yesterday",
          TRUE ~ "WSs Completed"
        )
      )
    
    current_wsids <- unique(surveyor_ws_current$wsid)
    
    surveyor_ws_unmapped <- ws_daily %>%
      filter(community %in% surveyor_communities,
             !wsid %in% current_wsids,
             !is.na(gps_location)) %>%
      group_by(wsid) %>%
      arrange(desc(survey_date)) %>%
      slice(1) %>%
      ungroup() %>%
      separate(gps_location, into = c("latitude", "longitude", "altitude", "accuracy"),
               sep = " ", remove = FALSE, convert = TRUE) %>%
      filter(!is.na(latitude), !is.na(longitude)) %>%
      st_as_sf(coords = c("longitude", "latitude"), crs = 4326)
    
    surveyor_ws_unmapped <- filter_within_buffer(surveyor_ws_unmapped) %>%
      mutate(category = "WS To Do")
  }
  
  # --- COUNTS & LABELS ---
  if (include_water_sources) {
    counts <- c(
      "WS Today" = nrow(surveyor_ws_current %>% filter(category == "WS Today")),
      "WS Yesterday" = nrow(surveyor_ws_current %>% filter(category == "WS Yesterday")),
      "WSs Completed" = nrow(surveyor_ws_current %>% filter(category == "WSs Completed")),
      "WS To Do" = nrow(surveyor_ws_unmapped),
      "HH Today" = nrow(surveyor_hh_current %>% filter(category == "HH Today")),
      "HH Yesterday" = nrow(surveyor_hh_current %>% filter(category == "HH Yesterday")),
      "HHs Completed" = nrow(surveyor_hh_current %>% filter(category == "HHs Completed")),
      "HH To Do" = nrow(surveyor_hh_unmapped)
    )
    ws_completed <- counts["WS Today"] + counts["WS Yesterday"] + counts["WSs Completed"]
    ws_total <- ws_completed + counts["WS To Do"]
  } else {
    counts <- c(
      "HH Today" = nrow(surveyor_hh_current %>% filter(category == "HH Today")),
      "HH Yesterday" = nrow(surveyor_hh_current %>% filter(category == "HH Yesterday")),
      "HHs Completed" = nrow(surveyor_hh_current %>% filter(category == "HHs Completed")),
      "HH To Do" = nrow(surveyor_hh_unmapped)
    )
  }
  
  hh_completed <- counts["HH Today"] + counts["HH Yesterday"] + counts["HHs Completed"]
  hh_total <- hh_completed + counts["HH To Do"]
  
  if (include_water_sources) {
    subtitle_text <- paste0(selected_surveyor, " - HH = ", hh_completed, "/", hh_total,
                            ", WS = ", ws_completed, "/", ws_total)
  } else {
    subtitle_text <- paste0(selected_surveyor, " - HH = ", hh_completed, "/", hh_total)
  }
  
  if (include_water_sources) {
    category_labels <- c(
      "WS Today" = paste0("WS Today (", counts["WS Today"], ")"),
      "WS Yesterday" = paste0("WS Yesterday (", counts["WS Yesterday"], ")"),
      "WSs Completed" = paste0("WSs Completed (", counts["WSs Completed"], ")"),
      "WS To Do" = paste0("WS To Do (", counts["WS To Do"], ")"),
      "HH Today" = paste0("HH Today (", counts["HH Today"], ")"),
      "HH Yesterday" = paste0("HH Yesterday (", counts["HH Yesterday"], ")"),
      "HHs Completed" = paste0("HHs Completed (", counts["HHs Completed"], ")"),
      "HH To Do" = paste0("HH To Do (", counts["HH To Do"], ")")
    )
    category_colors <- c(
      "WS Today" = "#0000FF", "WS Yesterday" = "#00FF00", "WSs Completed" = "#808080", "WS To Do" = "#FF7F00",
      "HH Today" = "#0000FF", "HH Yesterday" = "#00FF00", "HHs Completed" = "#808080", "HH To Do" = "#FF7F00"
    )
    category_shapes <- c(
      "WS Today" = 24, "WS Yesterday" = 24, "WSs Completed" = 24, "WS To Do" = 24,
      "HH Today" = 21, "HH Yesterday" = 21, "HHs Completed" = 21, "HH To Do" = 21
    )
  } else {
    category_labels <- c(
      "HH Today" = paste0("HH Today (", counts["HH Today"], ")"),
      "HH Yesterday" = paste0("HH Yesterday (", counts["HH Yesterday"], ")"),
      "HHs Completed" = paste0("HHs Completed (", counts["HHs Completed"], ")"),
      "HH To Do" = paste0("HH To Do (", counts["HH To Do"], ")")
    )
    category_colors <- c(
      "HH Today" = "#0000FF", "HH Yesterday" = "#00FF00", "HHs Completed" = "#808080", "HH To Do" = "#FF7F00"
    )
    category_shapes <- c(
      "HH Today" = 21, "HH Yesterday" = 21, "HHs Completed" = 21, "HH To Do" = 21
    )
  }
  
  # --- BUILD MAP ---
  p <- ggplot() +
    annotation_map_tile(type = "osm", zoomin = 0, progress = "none")
  
  for (shapefile in shapefiles_list) {
    p <- p + geom_sf(data = shapefile, fill = NA, color = "black", linewidth = 1)
  }
  
  if (include_water_sources) {
    if (nrow(surveyor_ws_current) > 0)
      p <- p + geom_sf(data = surveyor_ws_current, aes(fill = category, shape = category),
                        color = "black", size = 3, stroke = 1)
    if (nrow(surveyor_ws_unmapped) > 0)
      p <- p + geom_sf(data = surveyor_ws_unmapped, aes(fill = category, shape = category),
                        color = "black", size = 1.5, stroke = 0.5)
  }
  
  if (nrow(surveyor_hh_current) > 0)
    p <- p + geom_sf(data = surveyor_hh_current, aes(fill = category, shape = category),
                      color = "black", size = 3, stroke = 1)
  if (nrow(surveyor_hh_unmapped) > 0)
    p <- p + geom_sf(data = surveyor_hh_unmapped, aes(fill = category, shape = category),
                      color = "black", size = 1.5, stroke = 0.5)
  
  p <- p +
    scale_fill_manual(values = category_colors, labels = category_labels) +
    scale_shape_manual(values = category_shapes, labels = category_labels) +
    labs(subtitle = subtitle_text, fill = NULL, shape = NULL) +
    theme_minimal() +
    theme(axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          legend.position = "top") +
    guides(fill = guide_legend(nrow = 2, byrow = TRUE, override.aes = list(size = 3)),
           shape = guide_legend(nrow = 2, byrow = TRUE, override.aes = list(size = 3)))
  
  p
}
```

## Abdulai K
```{r map-abdulai-k, fig.width=5, fig.height=10}
surveyor_map("Abdulai K")
```

## Jamiatu
```{r map-jamiatu, fig.width=8, fig.height=8}
surveyor_map("Jamiatu")
```

## Boboieh
```{r map-boboieh, fig.width=8, fig.height=8}
surveyor_map("Boboieh")
```

## Musa
```{r map-musa, fig.width=5, fig.height=10}
surveyor_map("Musa")
```

# Missing HHs

```{r missing_hh_function}
missing_hh_table <- function(surveyor) {
  current_month_hhids <- hh_daily %>%
    filter(month(survey_date) == month(Sys.Date()),
           year(survey_date) == year(Sys.Date()),
           !is.na(hhid)) %>%
    distinct(hhid) %>%
    pull(hhid)
  
  hh_daily %>%
    filter(!is.na(hhid),
           !hhid %in% current_month_hhids,
           resp_surveyor == surveyor) %>%
    group_by(hhid) %>%
    arrange(desc(survey_date)) %>%
    slice(1) %>%
    ungroup() %>%
    mutate(
      survey_date = format(survey_date, "%b"),
      number = gsub("\n", " ", number)
    ) %>%
    select(hhid, zone, name, number, survey_date) %>%
    rename(HHID = hhid, Zone = zone, Name = name, Number = number, `Last Survey` = survey_date) %>%
    arrange(Zone, HHID) %>%
    kable(escape = TRUE, format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}

missing_hh_count <- function(surveyor) {
  current_month_hhids <- hh_daily %>%
    filter(month(survey_date) == month(Sys.Date()),
           year(survey_date) == year(Sys.Date()),
           !is.na(hhid)) %>%
    distinct(hhid) %>%
    pull(hhid)
  
  hh_daily %>%
    filter(!is.na(hhid),
           !hhid %in% current_month_hhids,
           resp_surveyor == surveyor) %>%
    distinct(hhid) %>%
    nrow()
}
```

## Abdulai K (`r missing_hh_count("Abdulai K")` remaining)
```{r missing_hh_abdulai_k}
missing_hh_table("Abdulai K")
```

## Jamiatu (`r missing_hh_count("Jamiatu")` remaining)
```{r missing_hh_jamiatu}
missing_hh_table("Jamiatu")
```

## Boboieh (`r missing_hh_count("Boboieh")` remaining)
```{r missing_hh_boboieh}
missing_hh_table("Boboieh")
```

## Musa (`r missing_hh_count("Musa")` remaining)
```{r missing_hh_musa}
missing_hh_table("Musa")
```

```{r diagnostics, results='asis'}
missing_hhid <- hh_current %>% filter(is.na(hhid))
duplicate_hhid <- hh_current %>%
  filter(!is.na(hhid)) %>%
  count(hhid, community) %>%
  filter(n > 1)
month_mismatch <- hh_daily %>%
  filter(!is.na(hhid),
         survey_date >= floor_date(Sys.Date(), "month")) %>%
  mutate(expected_month = format(survey_date, "%b")) %>%
  filter(as.character(survey_month) != expected_month)

if (nrow(missing_hhid) > 0) {
  cat("**⚠ Surveys without HHIDs this month:**", nrow(missing_hhid), "\n\n")
  missing_hhid %>%
    select(uuid, hhid, surveyor_name, name, number) %>%
    kable(format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
    cat()
  cat("\n\n")
}
if (nrow(duplicate_hhid) > 0) {
  cat("**⚠ Duplicate HHIDs this month:**", nrow(duplicate_hhid), "\n\n")
  hh_current %>%
    filter(hhid %in% duplicate_hhid$hhid) %>%
    select(uuid, hhid, surveyor_name, name, number) %>%
    kable(format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
    cat()
  cat("\n\n")
}
if (nrow(month_mismatch) > 0) {
  cat("**⚠ Survey month mismatches this month:**", nrow(month_mismatch), "\n\n")
  month_mismatch %>%
    select(uuid, hhid, surveyor_name, name, number) %>%
    kable(format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
    cat()
  cat("\n\n")
}
if (format(Sys.Date(), "%b") %in% c("Dec", "Feb", "Apr", "Jun", "Aug", "Oct")) knitr::knit_exit()
```

# Missing WSs

```{r ws_remaining_setup}
current_survey_month <- format(Sys.Date(), "%b")
is_survey_month <- !(current_survey_month %in% c("Dec", "Feb", "Apr", "Jun", "Aug", "Oct"))
remaining_sources <- function(data, comm, survey_month) {
  already_done <- data %>%
    filter(community == comm, display_month == survey_month) %>%
    pull(wsid)
  
  data %>%
    filter(community == comm, !is.na(wsid), !wsid %in% already_done) %>%
    arrange(wsid, desc(as.numeric(display_month))) %>%
    group_by(wsid) %>%
    slice(1) %>%
    ungroup() %>%
    select(wsid, uuid, display_month, respondent_name, zone, water_source_type) %>%
    arrange(zone, wsid)
}

remaining_count <- function(data, comm, survey_month) {
  nrow(remaining_sources(data, comm, survey_month))
}
```

## Cockle Bay (`r remaining_count(ws_daily, "Cockle Bay", current_survey_month)` remaining)

```{r, eval=is_survey_month}
if (!is.na(current_survey_month)) {
  remaining_sources(ws_daily, "Cockle Bay", current_survey_month) %>%
    kable(caption = paste0("Cockle Bay: Water sources not yet surveyed (", current_survey_month, ")")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

## Dworzark (`r remaining_count(ws_daily, "Dworzark", current_survey_month)` remaining)

```{r, eval=is_survey_month}
if (!is.na(current_survey_month)) {
  remaining_sources(ws_daily, "Dworzark", current_survey_month) %>%
    kable(caption = paste0("Dworzark: Water sources not yet surveyed (", current_survey_month, ")")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

## Portee Rokupa (`r remaining_count(ws_daily, "Portee Rokupa", current_survey_month)` remaining)

```{r, eval=is_survey_month}
if (!is.na(current_survey_month)) {
  remaining_sources(ws_daily, "Portee Rokupa", current_survey_month) %>%
    kable(caption = paste0("Portee Rokupa: Water sources not yet surveyed (", current_survey_month, ")")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```
